---
title: "Kisoken2016:Speaking Anxiety"
author: "Yu Tamura"
date: "March 18, 2017"
output: 
  html_document:
    toc: true
    number_section: true

---

This document describes the analysis of speaking anxiety data reporeted in Tamura (2017).

###Prepare necessary packages
```{r,eval=F}
#If you haven't installed the packages, please install first. If you have, you don't need to install the packages
install.packages("dplyr")
install.packages("mice")
install.packages("VIM")
install.packages("psychometric")
install.packages("psych")
install.packages("rlist")
install.packages("coin")
```
```{r,message=F,warning=F}
#Read packages
library(dplyr)
library(mice)
library(VIM)
library(psychometric)
library(psych)
library(rlist)
library(coin)
```

#Read the data
```{r}
april<-read.csv("Data/H27_speaking-anxiety_April.csv",header=T,sep=",")
july<-read.csv("Data/H27_speaking-anxiety_July.csv",header=T,sep=",")
big5<-read.csv("Data/H27_BIG5_results.csv",header=T,sep = ",")
```

#Check the students who demonstrate no variance for all the responses
```{r}
april$var<-apply(april[,-1],1,var)
july$var<-apply(july[,-1],1,var)

april%>%
  filter(var==0)%>%
  dplyr::select(ID)

july%>%
  filter(var==0)%>%
  dplyr::select(ID)

```
In the April data two students showed no variance, which means these two students marked the same number for all the items. Therefore, treat the responses as NAs. In the July data, no such student was observed.

```{r}
april2<-april #copy the data
april2%>%
  dplyr::filter(ID=="9")%>%
  dplyr::select(ability.1.ap:avoid.3.ap)%>%
  replace(.,values=NA)->april2[9,c(2:(ncol(april2)-1))]

april2%>%
  dplyr::filter(ID=="19")%>%
  dplyr::select(ability.1.ap:avoid.3.ap)%>%
  replace(.,values=NA)->april2[19,c(2:(ncol(april2)-1))]

```

#Reliablity of the measurement
```{r}
alpha(april2[,-c(1,11)]) #All items
alpha(july[,-c(1,11)]) #All items

#Ability in April
april2%>%
  dplyr::select(starts_with("ability"))%>%
  alpha
#Anxiety in April
april2%>%
  dplyr::select(starts_with("anxiety"))%>%
  alpha

#Avoidance in April
april2%>%
  dplyr::select(starts_with("avoid"))%>%
  alpha

#Ability in July
july%>%
  dplyr::select(starts_with("ability"))%>%
  alpha
#Anxiety in July
july%>%
  dplyr::select(starts_with("anxiety"))%>%
  alpha

#Avoidance in July
july%>%
  dplyr::select(starts_with("avoid"))%>%
  alpha

```

#Combine the April and July data into one data frame
```{r}
cbind(april2[,-11],july[,-c(1,11)],big5[,-1])%>% #exclude ID column and var column
  as.data.frame->dat
#dat
dat[,-1]->noID #making the data without ID column
summary(noID)
```

#Check the missing data
```{r}
noID%>%
  dplyr::select(ability.1.ap:avoid.3.jul)%>%
  aggr%>%
  summary
```

#Multiple Imputation by mice
```{r}
m<-20 #define the numer of data sets to be created
imp_data<-mice(noID,m,method="pmm",printFlag = F,maxit = 50,seed = 1)
```

#Summarize the data 
Since the imputed data sets were not summarized as three sub-components (ability, anxiety, avoidance), we need to calculate the mean scores of each sub-component. 

####Prepare lists and data frames
```{r}
imp_list<-list() #prepare a list
imp_list$april<-list() #prepare a list for April data
imp_list$april$all<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for all items
imp_list$april$ability<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for ability
imp_list$april$anxiety<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for anxiety
imp_list$april$avoid<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for avoidance

imp_list$july<-list() #prepare a list for July data
imp_list$july$all<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for all items
imp_list$july$ability<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for ability
imp_list$july$anxiety<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for anxiety
imp_list$july$avoid<-matrix(nrow = nrow(noID),ncol=m) #prepare a data frame for avoidance

```

##All items
```{r}
#April
for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(ends_with("ap"))%>%
    apply(.,1,mean)->imp_list$april$all[,i]
}

#July
for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(ends_with("jul")) %>%
    apply(.,1,mean)->imp_list$july$all[,i]
}

```

###Descriptive Statistics (All items)
```{r}
apply(imp_list$april$all,1,mean)%>%describe #April
apply(imp_list$july$all,1,mean)%>%describe #July
```

##Ability
```{r}
for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("ability"))%>%
    dplyr::select(ends_with("ap")) %>%
    apply(.,1,mean)->imp_list$april$ability[,i]
}

for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("ability"))%>%
    dplyr::select(ends_with("jul")) %>%
    apply(.,1,mean)->imp_list$july$ability[,i]
}

```

###Descriptive Statistics (Ability)
```{r}
apply(imp_list$april$ability,1,mean)%>%describe #April
apply(imp_list$july$ability,1,mean)%>%describe #July
```

##Anxiety
```{r}
for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("anxiety"))%>%
    dplyr::select(ends_with("ap")) %>%
    apply(.,1,mean)->imp_list$april$anxiety[,i]
}

for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("anxiety"))%>%
    dplyr::select(ends_with("jul")) %>%
    apply(.,1,mean)->imp_list$july$anxiety[,i]
}

```

###Descriptive Statistics (Anxiety)
```{r}
apply(imp_list$april$anxiety,1,mean)%>%describe #April
apply(imp_list$july$anxiety,1,mean)%>%describe #July
```

##Avoidance
```{r}
for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("avoid"))%>%
    dplyr::select(ends_with("ap")) %>%
    apply(.,1,mean)->imp_list$april$avoid[,i]
}

for (i in 1:m){
  mice::complete(imp_data,i)%>%
    dplyr::select(starts_with("avoid"))%>%
    dplyr::select(ends_with("jul")) %>%
    apply(.,1,mean)->imp_list$july$avoid[,i]
}

```

###Descriptive Statistics (Avoidance)
```{r}
apply(imp_list$april$avoid,1,mean)%>%describe #April
apply(imp_list$july$avoid,1,mean)%>%describe #July
```

##Check normality
```{r}
normal<-list()
normal$april$all<-apply(imp_list$april$all,2,shapiro.test) #All items for April
normal$july$all<-apply(imp_list$july$all,2,shapiro.test) #All items for July

normal$april$ability<-apply(imp_list$april$ability,2,shapiro.test) #Ability for April
normal$july$ability<-apply(imp_list$july$ability,2,shapiro.test) #Ability for July

normal$april$anxiety<-apply(imp_list$april$anxiety,2,shapiro.test) #Anxiety for April
normal$july$anxiety<-apply(imp_list$july$anxiety,2,shapiro.test) #Anxiety for July

normal$april$avoid<-apply(imp_list$april$avoid,2,shapiro.test) #Avoidance for April
normal$april$avoid<-apply(imp_list$july$avoid,2,shapiro.test) #Avoidance for July
```

##Check how many data sets violate normality
```{r}
list.filter(normal$april$all,p.value<.05)%>%length #All items for April
list.filter(normal$july$all,p.value<.05)%>%length #All items for July
list.filter(normal$april$ability,p.value<.05)%>%length #Ability for April
list.filter(normal$july$ability,p.value<.05)%>%length #Ability for July
list.filter(normal$april$anxiety,p.value<.05)%>%length #Anxiety for April
list.filter(normal$july$anxiety,p.value<.05)%>%length #Anxiety for July
list.filter(normal$april$avoid,p.value<.05)%>%length #Avoidance for April
list.filter(normal$july$avoid,p.value<.05)%>%length #Avoidance for July

```

We can see that some of the data sets for the Ability in April showed p values lower than .05 in the Shapiro-Wilk normality test, indicating that these were not normaliy distributed. In addition, all the data sets for the Anxiety in April were also not normality distributed. Therefore, for those data sets, we are going to perform non-parametric Wilkoxon Singed Rank Tests as well.


#Paired sample t-tests
##All items
```{r}
r.all<-data.frame(t=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m)) #prepare a data frame
#print(r.anxiety)

#Repeat paired sample t-tests.
for (i in 1:m){
  result<-0
  result<-t.test(imp_list$april$all[,i],imp_list$july$all[,i],paired = T) #perform t-test
  t<-0
  t<-result$statistic #get t-value
  p<-result$p.value #get p-value
  r.all[i,1]<-round(t,3)
  r.all[i,2]<-p
  df<-0
  df<-result$parameter #get degree of freedom
  r<-0
  r<-sqrt((t^2)/(t^2+df)) #get effect size r
  r.all[i,3]<-r
  r.all[i,4:5]<-CIr(r = r,n = df+1,0.95) #get 95%CI
}
print(r.all)
apply(r.all,2,mean)%>%round(.,3)
```

##Ability
###Wilcoxsign_test
```{r}
wilcox.result.ability<-data.frame(z.score=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m))
for (i in 1:m){
  result<-0  
  result<-wilcoxsign_test(imp_list$april$ability[,i]~imp_list$july$ability[,i],distribution="exact")
  wilcox.result.ability[i,1] <- result@statistic@teststatistic #extract z score
  wilcox.result.ability[i,2] <- pvalue(result) #p value for the test
  wilcox.result.ability[i,3] <- wilcox.result.ability[i,1]/sqrt(nrow(imp_list$july$ability)) #effect size r
  wilcox.result.ability[i,4:5] <- CIr(r = wilcox.result.ability[i,3],n = nrow(imp_list$july$ability),0.95)
}
print(wilcox.result.ability)
apply(wilcox.result.ability,2,mean)%>%round(.,3)
```

###Paired Sample t-tests
```{r}
r.ability<-data.frame(t=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m)) #prepare a data frame
#print(r.anxiety)

#Repeat paired sample t-tests.
for (i in 1:m){
  result<-0
  result<-t.test(imp_list$april$ability[,i],imp_list$july$ability[,i],paired = T) #perform t-test
  t<-0
  t<-result$statistic #get t-value
  p<-result$p.value #get p-value
  r.ability[i,1]<-round(t,3)
  r.ability[i,2]<-p
  df<-0
  df<-result$parameter #get degree of freedom
  r<-0
  r<-sqrt((t^2)/(t^2+df)) #get effect size r
  r.ability[i,3]<-r
  r.ability[i,4:5]<-CIr(r = r,n = df+1,0.95) #get 95%CI
}
print(r.ability)
apply(r.ability,2,mean)%>%round(.,3)
```

##Anxiety
###Wilcoxsign_test
```{r}
wilcox.result.anxiety<-data.frame(z.score=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m))
for (i in 1:m){
  result<-0  
  result<-wilcoxsign_test(imp_list$april$anxiety[,i]~imp_list$july$anxiety[,i],distribution="exact")
  wilcox.result.anxiety[i,1] <- result@statistic@teststatistic #extract z score
  wilcox.result.anxiety[i,2] <- pvalue(result) #p value for the test
  wilcox.result.anxiety[i,3] <- wilcox.result.anxiety[i,1]/sqrt(nrow(imp_list$july$anxiety)) #effect size r
  wilcox.result.anxiety[i,4:5] <- CIr(r = wilcox.result.anxiety[i,3],n = nrow(imp_list$july$anxiety),0.95)
}
print(wilcox.result.anxiety)
apply(wilcox.result.anxiety,2,mean)%>%round(.,3)
```

###Paired Sample t-tests
```{r}
r.anxiety<-data.frame(t=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m)) #prepare a data frame
#print(r.anxiety)

#Repeat paired sample t-tests.
for (i in 1:m){
  result<-0
  result<-t.test(imp_list$april$anxiety[,i],imp_list$july$anxiety[,i],paired = T) #perform t-test
  t<-0
  t<-result$statistic #get t-value
  p<-result$p.value #get p-value
  r.anxiety[i,1]<-round(t,3)
  r.anxiety[i,2]<-p
  df<-0
  df<-result$parameter #get degree of freedom
  r<-0
  r<-sqrt((t^2)/(t^2+df)) #get effect size r
  r.anxiety[i,3]<-r
  r.anxiety[i,4:5]<-CIr(r = r,n = df+1,0.95) #get 95%CI
}
print(r.anxiety)
apply(r.anxiety,2,mean)%>%round(.,3)
```

##Avoidance
```{r}
r.avoid<-data.frame(t=rep(0,m),p.value=rep(0,m),r=rep(0,m),LowerCI=rep(0,m),UpperCI=rep(0,m)) #prepare a data frame
#print(r.anxiety)

#Repeat paired sample t-tests.
for (i in 1:m){
  result<-0
  result<-t.test(imp_list$april$avoid[,i],imp_list$july$avoid[,i],paired = T) #perform t-test
  t<-0
  t<-result$statistic #get t-value
  p<-result$p.value #get p-value
  r.avoid[i,1]<-round(t,3)
  r.avoid[i,2]<-p
  df<-0
  df<-result$parameter #get degree of freedom
  r<-0
  r<-sqrt((t^2)/(t^2+df)) #get effect size r
  r.avoid[i,3]<-r
  r.avoid[i,4:5]<-CIr(r = r,n = df+1,0.95) #get 95%CI
}
print(r.avoid)
apply(r.avoid,2,mean)%>%round(.,3)

r.avoid$LowerCI[r.avoid$LowerCI< 0]%>%length
r.avoid$p.value[r.avoid$p.value< .05]%>%length
```

#Visualization
##All items
```{r,fig.align="center",fig.height=5,fig.width=5}
plot(apply(imp_list$april$all,1,mean),apply(imp_list$july$all,1,mean)
     ,xlab="April",ylab="July"
     ,xlim=c(0,7),ylim=c(0,7)
     ,main="All items")
abline(0,1)
```

##Ability
```{r,fig.align="center",fig.height=5,fig.width=5}
plot(apply(imp_list$april$ability,1,mean),apply(imp_list$july$ability,1,mean)
     ,xlab="April",ylab="July"
     ,xlim=c(0,7),ylim=c(0,7)
     ,main="Competence")
abline(0,1)
```

##Anxiety
```{r,fig.align="center",fig.height=5,fig.width=5}
plot(apply(imp_list$april$anxiety,1,mean),apply(imp_list$july$anxiety,1,mean)
     ,xlab="April",ylab="July"
     ,xlim=c(0,7),ylim=c(0,7)
     ,main="Anxiety")
abline(0,1)

```

##Avoidance
```{r,fig.align="center",fig.height=5,fig.width=5}
plot(apply(imp_list$april$avoid,1,mean),apply(imp_list$july$avoid,1,mean)
     ,xlab="April",ylab="July"
     ,xlim=c(0,7),ylim=c(0,7)
     ,main="Avoidance")
abline(0,1)

```

***

#List-wise deletion (Just for reference)
```{r}
noID%>%
  na.exclude%>%
  dplyr::select(ability.1.ap:avoid.3.jul)->listwise.dat
```
##Stats
```{r}
listwise.dat2<-data.frame(ability.ap=rep(0,nrow(listwise.dat)),
                          anxiety.ap=rep(0,nrow(listwise.dat)),
                          avoid.ap=rep(0,nrow(listwise.dat)),
                          all.ap=rep(0,nrow(listwise.dat)),
                          ability.jul=rep(0,nrow(listwise.dat)),
                          anxiety.jul=rep(0,nrow(listwise.dat)),
                          avoid.jul=rep(0,nrow(listwise.dat)),
                          all.jul=rep(0,nrow(listwise.dat)))
listwise.dat%>%
  dplyr::select(starts_with("ability")) %>%
  dplyr::select(ends_with("ap"))%>%
  apply(.,1,mean)->listwise.dat2$ability.ap

listwise.dat%>%
  dplyr::select(starts_with("anxiety")) %>%
  dplyr::select(ends_with("ap"))%>%
  apply(.,1,mean)->listwise.dat2$anxiety.ap

listwise.dat%>%
  dplyr::select(starts_with("avoid")) %>%
  dplyr::select(ends_with("ap"))%>%
  apply(.,1,mean)->listwise.dat2$avoid.ap

listwise.dat%>%
  dplyr::select(ends_with("ap"))%>%
  apply(.,1,mean)->listwise.dat2$all.ap
  
listwise.dat%>%
  dplyr::select(starts_with("ability")) %>%
  dplyr::select(ends_with("jul"))%>%
  apply(.,1,mean)->listwise.dat2$ability.jul

listwise.dat%>%
  dplyr::select(starts_with("anxiety")) %>%
  dplyr::select(ends_with("jul"))%>%
  apply(.,1,mean)->listwise.dat2$anxiety.jul

listwise.dat%>%
  dplyr::select(starts_with("avoid")) %>%
  dplyr::select(ends_with("jul"))%>%
  apply(.,1,mean)->listwise.dat2$avoid.jul

listwise.dat%>%
  dplyr::select(ends_with("jul"))%>%
  apply(.,1,mean)->listwise.dat2$all.jul

sapply(listwise.dat2,describe,simplify = T)%>%t()
```

##Paired _t_-tests
```{r}
head(listwise.dat2)
#apply(listwise.dat2,2,shapiro.test)

t.test(listwise.dat2$all.ap,listwise.dat2$all.jul,paired=T)
t.test(listwise.dat2$ability.ap,listwise.dat2$ability.jul,paired=T)
t.test(listwise.dat2$anxiety.ap,listwise.dat2$anxiety.jul,paired=T)
t.test(listwise.dat2$avoid.ap,listwise.dat2$avoid.jul,paired=T)

wilcoxsign_test(listwise.dat2$all.ap~listwise.dat2$all.jul,exact=T)
wilcoxsign_test(listwise.dat2$ability.ap~listwise.dat2$ability.jul,exact=T)
wilcoxsign_test(listwise.dat2$anxiety.ap~listwise.dat2$anxiety.jul,exact=T)
wilcoxsign_test(listwise.dat2$avoid.ap~listwise.dat2$avoid.jul,exact=T)

```

***

#Identify the students whose speaking anxiety did not decrease
```{r}
#Prepare a data frame 
deacreasing<-data.frame(all=rep(0,nrow(imp_list$april$all))
                        ,ability=rep(0,nrow(imp_list$april$ability))
                        ,anxiety=rep(0,nrow(imp_list$april$anxiety))
                        ,avoid=rep(0,nrow(imp_list$april$avoid)))

#Decreased -> FALSE; Not decreased -> TRUE
deacreasing$all<-apply(imp_list$april$all,1,mean)<= apply(imp_list$july$all,1,mean)
deacreasing$ability<-apply(imp_list$april$ability,1,mean) <= apply(imp_list$july$ability,1,mean)
deacreasing$anxiety<-apply(imp_list$april$anxiety,1,mean) <= apply(imp_list$july$anxiety,1,mean)
deacreasing$avoid<-apply(imp_list$april$avoid,1,mean) <= apply(imp_list$july$avoid,1,mean)

grep(TRUE,deacreasing$all) #Extracting the rows which has TRUE
grep(TRUE,deacreasing$ability) #Extracting the rows which has TRUE
grep(TRUE,deacreasing$anxiety) #Extracting the rows which has TRUE
grep(TRUE,deacreasing$avoid) #Extracting the rows which has TRUE
```

Category   | ID
-----------|------
All items  |`r grep(TRUE,deacreasing$all)`
Competence |`r grep(TRUE,deacreasing$ability)`
Anxiety    |`r grep(TRUE,deacreasing$anxiety)`
Avoidance  |`r grep(TRUE,deacreasing$avoid)`
